\documentclass[12pt]{article}
\usepackage{amsfonts}
\usepackage[hscale=0.8,vscale=0.8]{geometry}
\usepackage{hyperref}
\usepackage{amsmath}

\allowdisplaybreaks

\begin{document}

\title{Notes on Quadratic Gaussian Model}
\date{Dec. 32, 2999}

\maketitle


\section{The Quadratic Gaussian Model}

  The quadratic Gaussian model can be obtained by having the short rate in a quadratic form,
  \begin{equation}
    r(t)=z(t)^{\top}\gamma(t)z(t)+h(t)^{\top}z(t)+a(t),
    \label{quadGaussian}
  \end{equation}
  where $\gamma(t)$ is a $d\times d$ symmetric matrix, $h(t)$ is a $d$-dimensional vector, and $a(t)$ is
  used to fit the initial yield curve. Here, the $d$-dimensional state variable $z(t)$ satisfies
  \begin{equation}
    dz(t)=g(t)^{\top}dW(t), \quad \quad z(0)=0,
  \end{equation}
  where $W(t)$ is a $d$-dimensional Brownian motion.

  \subsection{Relation to the Affine Model}

  To see the connection to the affine model, consider the one dimensional constant parameter case.
  In this case, Eq. (\ref{quadGaussian}) reduces to
  \begin{equation}
    r(t)=\gamma z^2(t)+hz(t)+a,
  \end{equation}
  which can be solved,
  \begin{equation}
    z(t)=\frac{\sqrt{h^2+4\gamma\big(r(t)-a\big)}-h}{2},
  \end{equation}
  by keeping the positive root. Then, it can be shown
  \begin{equation}
    dr(t)=\frac{1}{\gamma}\sqrt{h^2+4\gamma\big(r(t)-a\big)}g(t)dW(t),
  \end{equation}
  which is clearly affine.

  \subsection{Analytical Results}

  Due to the affine nature of the quadratic Gaussian model, the discount bond price is similarly given
  in a quadratic form,
  \begin{equation}
    P(t,T)=\exp\Big(-z(t)^{\top}\gamma(t,T)z(t)-h(t,T)^{\top}z(t)-a(t,T)\Big).
  \end{equation}
  Applying the Feynman-Kac theorem, the discount bond price satisfies the following PDE,
  \begin{equation}
    \frac{\partial P}{\partial t}+\frac{1}{2}\sum_{ijk}
    \frac{\partial^2P}{\partial z_i\partial z_j}g_{ki}(t)g_{kj}(t)=r(t)P.
  \end{equation}
  Calculate the derivatives and match the $z$ terms on both sides of the above equation, we will
  obtain a system of Riccati ODEs,
  \begin{eqnarray}
    && -\frac{d}{dt}\gamma(t,T) + 2\gamma(t,T)g(t)^{\top}g(t)\gamma(t,T)=\gamma(t),\\
    && -\frac{d}{dt}h(t,T) + 2\gamma(t,T)g(t)^{\top}g(t)h(t,T)=h(t),\\
    && -\frac{d}{dt}a(t,T) - {\rm Tr}\Big(\gamma(t,T)g(t)^{\top}g(t)\Big) + \frac{1}{2}h(t,T)^{\top}g(t)^{\top}g(t)h(t,T)=a(t),
  \end{eqnarray}
  with terminal conditions $\gamma(T,T)=0$, $h(T,T)=0$, and $a(T,T)=0$.



\begin{thebibliography}{1}

  \bibitem{AP} Leif Andersen and Vladimir Piterbarg, {\it Interest Rate Modeling}, Atlantic Financial Press, 2010.

\end{thebibliography}

\end{document}