\documentclass[12pt]{article}
\usepackage{amsfonts}
\usepackage[hscale=.8,vscale=.8]{geometry}
\usepackage{hyperref}

\begin{document}

\title{Notes on Feller Condition}
\date{Dec. 32, 2999}

\maketitle

\section{Fokker-Planck Equation}

  Consider the following parabolic partial differential equation (PDE) \cite{Feller}
  \begin{equation}
    \frac{\partial u(t,x)}{\partial t} = -\frac{\partial}{\partial x}\left((bx+c)u(t,x)\right)
                                       + \frac{\partial^2}{\partial x^2}\left(axu(t,x)\right),
    \label{FP}
  \end{equation}
  with $x>0$. This can be viewed as the corresponding Fokker-Planck equation for the Cox-Ingersoll-Ross (CIR)
  process
  \begin{equation}
    dx_t=\kappa(\theta-x_t)dt + \sigma\sqrt{x_t}dW_t,
  \end{equation}
  with $a=\sigma^2/2$, $b=-\kappa$, and $c=\kappa\theta$.

  We want to find the solution of the PDE (\ref{FP}), with certain initial condition. In particular, we are 
  interested in the fundamental solution of the PDE (\ref{FP}), {\it i.e.}, the initial condition is given
  by
  \begin{equation}
    u(0,x)=\delta(x-y),
  \end{equation}
  where $\delta(x)$ is the Dirac delta function. To this end, introduce the Laplace transform of $u(t,x)$ as
  \begin{equation}
    v(t,\lambda)=\int_0^{+\infty}e^{-\lambda x}u(t,x)dx,
  \end{equation}
  for $\lambda > 0$. We denote the Laplace transform of the initial condition as
  \begin{equation}
    \pi(\lambda) = \int_0^{+\infty}e^{-\lambda x}u(0,x)dx,
  \end{equation} 
  and for the fundamental solution, $\pi(\lambda) = e^{-\lambda y}$. Consider the Laplace transform of the right hand side of Eq. (\ref{FP}),
  \begin{eqnarray}
      && \int_0^{+\infty} e^{-\lambda x}\bigg[\big(axu(t,x)\big)_{xx}-\big((bx+c)u(t,x)\big)_x\bigg]dx \nonumber\\
    = && \left. e^{-\lambda x}\bigg[\big(axu(t,x)\big)_{x}-\big((bx+c)u(t,x)\big)\bigg]\right|_0^{+\infty}\nonumber\\
      && \quad\quad +\lambda \int_0^{+\infty} e^{-\lambda x}\bigg[\big(axu(t,x)\big)_{x}-\big((bx+c)u(t,x)\big)\bigg]dx \nonumber\\
    = && f(t) + \lambda(b-\lambda a)v_{\lambda} - c\lambda v,
  \end{eqnarray}
  where
  \begin{equation}
    f(t) = \lim_{x\rightarrow 0}\left[(bx+c)u-(axu)_x\right],
  \end{equation}
  is the flux at $x=0$ and cannot be arbitrarily specified.

  After the Laplace transform, Eq. (\ref{FP}) becomes
  \begin{equation}
    v_t + \lambda(\lambda a - b) v_{\lambda} = f(t) - c\lambda v.
  \end{equation}
  This first order PDE can be solved by the method of characteristics.


\begin{thebibliography}{99}
  \bibitem{Feller}
    W. Feller, {\it Two Singular Diffusion Problems}, Annals of Mathematics {\bf 54}, 173 (1951).

\end{thebibliography}


\end{document}